Unity in diversity: Children from 17 communities process gaze in similar ways

### 2024-01-23 paper/paper.tex
advance paper

\caption{\label{tab:tab1}Participant demographics.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lllllll}
\toprule
Continent & Country & Community & N(male) & Age (range) & Language & Touchscreen\\
\midrule
America & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & 0.90\\
 & Mexico & Ocuilan & 125 (61) & 4.97 (2.57 - 6.95) & Spanish (Mexican) & 0.77\\
 & USA & Stanford & 100 (56) & 5.00 (2.52 - 7.90) & English (American) & 0.98\\
Africa & Namibia & Hai||om & 60 (38) & 5.85 (2.74 - 8.34) & Hai||om & 0.05\\
 &  & Khwe & 59 (24) & 5.84 (3.38 - 8.63) & Khwedam & 0.19\\
\addlinespace
 &  & Windhoek & 41 (18) & 5.68 (2.66 - 8.66) & English (Nigerian) & 0.95\\
 & Nigeria & Akure & 114 (53) & 5.07 (2.57 - 7.33) & English (Nigerian) & 0.91\\
 & Rep. Congo & BaYaka & 28 (12) & 7.86 (3.94 - 10.56) & BaYaka & 1.00\\
 &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & 1.00\\
 & Sambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Bemba & 0.14\\
\addlinespace
 & Uganda & Nyabyeya & 51 (27) & 5.41 (3.27 - 8.21) & Swahili & 0.49\\
Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & 0.89\\
 & UK & Plymouth & 70 (30) & 6.02 (2.38 - 8.94) & English (British) & 0.99\\
Asia & China & Beijing & 123 (62) & 5.47 (2.69 - 8.48) & Mandarin & 0.95\\
 & India & Pune & 155 (75) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & 0.92\\
\addlinespace
 & Turkey & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & 1.00\\
Oceania & New Zealand & Auckland & 43 (19) & 5.14 (2.81 - 8.75) & English (New Zealand) & 0.95\\
\bottomrule
\end{tabular}}
\end{table}

@@

As the first step, we investigated developmental gains. Across all 17 communities, we found a substantial increase in average levels of precision with age (range: \(\beta_{min}\) = , 95\% CrI () to \(\beta_{max}\) = ()). There were marked differences between communities: urban communities around the globe showed higher levels of precision compared to rural communities. We return to this result below. However, differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision (e.g.~) performed better compared to some individuals from a setting with a very high average level of precision. Furthermore, in all communities, some 4-year-olds outperformed children two years older than them.

>>>>

\caption{\label{tab:tab1}Participant demographics.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llllllll}
\toprule
Continent & Country & Community & N(male) & Age (range) & Language & Market integration & Touchscreen\\
\midrule
America & Argentina & Buenos Aires & 105 (53) & 4.72 (3.00 - 6.96) & Spanish (Rioplatense) & high & 0.90\\
 & Mexico & Ocuilan & 125 (61) & 4.97 (2.57 - 6.95) & Spanish (Mexican) & medium & 0.77\\
 & USA & Stanford & 100 (56) & 5.00 (2.52 - 7.90) & English (American) & high & 0.98\\
Africa & Namibia & Hai||om & 60 (38) & 5.85 (2.74 - 8.34) & Hai||om & low & 0.05\\
 &  & Khwe & 59 (24) & 5.84 (3.38 - 8.63) & Khwedam & low & 0.19\\
\addlinespace
 &  & Windhoek & 41 (18) & 5.68 (2.66 - 8.66) & English (Nigerian) & high & 0.95\\
 & Nigeria & Akure & 114 (53) & 5.07 (2.57 - 7.33) & English (Nigerian) & high & 0.91\\
 & Rep. Congo & BaYaka & 28 (12) & 7.86 (3.94 - 10.56) & BaYaka & low & 0.00\\
 &  & Bandongo & 30 (11) & 7.45 (3.50 - 10.95) & Lingala & low & 0.00\\
 & Sambia & Chimfunshi & 22 (5) & 5.98 (2.88 - 8.00) & Bemba & medium & 0.14\\
\addlinespace
 & Uganda & Nyabyeya & 51 (27) & 5.41 (3.27 - 8.21) & Swahili & medium & 0.49\\
Europe & Germany & Leipzig & 100 (48) & 4.88 (2.53 - 6.95) & German & high & 0.89\\
 & UK & Plymouth & 70 (30) & 6.02 (2.38 - 8.94) & English (British) & high & 0.99\\
Asia & China & Beijing & 123 (62) & 5.47 (2.69 - 8.48) & Mandarin & high & 0.95\\
 & India & Pune & 155 (75) & 6.14 (3.06 - 8.83) & English (Indian) / Marathi & high & 0.92\\
\addlinespace
 & Turkey & Malatya & 85 (40) & 5.02 (2.75 - 7.12) & Turkish & high & 1.00\\
Oceania & New Zealand & Auckland & 43 (19) & 5.14 (2.81 - 8.75) & English (New Zealand) & high & 0.95\\
\bottomrule
\end{tabular}}
\end{table}

@@

As the first step, we investigated developmental gains. Across all 17 communities, we found a substantial increase in average levels of precision with age (range: \(\beta_{min}\) = , 95\% CrI () to \(\beta_{max}\) = ()). There were marked differences between communities: highly market-integrated communities around the globe showed higher levels of precision compared to less market-integrated communities. However, we think that these results are better explained by exposure to technology than market integration. We discuss them in more detail below. Differences between communities were small compared to differences between individuals: communities did not form homogeneous clusters but largely overlapping distributions in that some individuals from communities with a lower average level of precision performed better compared to some individuals from a setting with a very high average level of precision. Furthermore, in all communities, some 4-year-olds outperformed children two years older than them (see Fig. \ref{fig:fig2}).

{\centering \includegraphics[width=0.75\linewidth]{../visuals/pvis_pred}

\caption{A) Developmental trajectories by cultural settings. Transparent dots show aggregated data for each individual. The color dentoes the different cultural settings. The developmental trajectories are predicted based on a model of the data aggregated for each participant. B) Performance by screen section and cultural setting. Each bin covers 1/10th of the screen. Points show means and eroor bars 95\% confidence intervals for the data within that bin aggregated across participants.}\label{fig:fig2}
\end{figure}
